SFJ: An implementation of Semantic Featherweight Java

### 2020-02-27 conference/paper.tex
fix typo

We instead only implement the \emph{diagonal} method on polygons that support it. We can then specify to only accept classes that implement the method \emph{diagonal}. If we pass an argument of type \emph{Triangle}, it is not in the computed set of subtypes, so we get a type checking error at compile time.
We do not have to generate a relation for all methods in all classes as this is computationally unnecessary and instead
only generate the set of subtypes on encountering a method type.

>>>>

We instead only implement the \emph{getDiagonal} method on polygons that support it. We can then specify to only accept classes that implement the method \emph{getDiagonal}. If we pass an argument of type \emph{Triangle}, it is not in the computed set of subtypes, so we get a type checking error at compile time.
We do not have to generate a relation for all methods in all classes as this is computationally unnecessary and instead
only generate the set of subtypes on encountering a method type.
